Example with One simulated data

### 2023-11-16 Docs/SimExample.Rmd
add numeric stability to example file

```{r pred_debias_unscale, results='hide'}
# approximation process
# container
pred_list <- list()
test_id <- unique(test_df$id)

@@

    # fit laplace approximation
    Fit <- LaplaceApproximation(Model, parm = rep(0, K), 
                                Data=MyData, Method = "BFGS")
    # individual score
    score <- Fit$Summary1[, "Mode"]

@@

```
## Prediction with scaled eigenfunctions and eigenvalues

```{r pred_debias_scale, results='hide'}
# container
pred_list2 <- list()

@@

    # fit laplace approximation
    Fit <- LaplaceApproximation(Model, parm = rep(0, K), Data=MyData, Method = "BFGS")
    score <- Fit$Summary1[, "Mode"]

@@

>>>>

```{r pred_debias_unscale, results='hide'}
# approximation process
# container
pred_list <- list()
test_id <- unique(test_df$id)
converge_vec <- matrix(NA, N_test, 4) # convergence status

@@

    # fit laplace approximation
    Fit <- LaplaceApproximation(Model, parm = rep(0, K), 
                                Data=MyData, Method = "BFGS")
    converge_vec[i, which(c(0.2, 0.4, 0.6, 0.8)==tmax)] <- Fit$Converged
    # individual score
    score <- Fit$Summary1[, "Mode"]

@@

## Prediction with scaled eigenfunctions and eigenvalues

```{r pred_debias_scale, results='hide'}
# container
pred_list2 <- list()
converge_vec2 <- matrix(NA, N_test, 4)

@@

    # fit laplace approximation
    Fit <- LaplaceApproximation(Model, parm = rep(0, K), Data=MyData, Method = "BFGS")
    converge_vec2[i, which(c(0.2, 0.4, 0.6, 0.8)==tmax)] <- Fit$Converged
    score <- Fit$Summary1[, "Mode"]

@@

## Numeric stability

I start by looking at the convergence rate of scaled and un-scaled estimates:

- unscaled: `r round(mean(converge_vec), 2)`
- scaled: `r round(mean(converge_vec2), 2)`

Then, I would like to see some individuals who performed the most different under the two set of estimates. I used the observations up to 0.4 as an example, since it is the most problematic scenario.

Below I identify the subjects with most dependency in prediction

```{r}
# subjects with the most difference in prediction
diff_subjs <- full_join(df_pred %>% select(id, t, pred0.4),
          df_pred2 %>% select(id, t, pred0.4),
          by = c("id", "t")) %>% 
  mutate(diff = (pred0.4.x-pred0.4.y)^2) %>%
  group_by(id) %>%
  summarise(diff = sum(diff, na.rm = T)) %>% 
  arrange(desc(diff)) %>% 
  head(10)
```

Now I look at there convergence status

- unscaled:

```{r}
converge_vec[diff_subjs$id,  2]
```

- scaled:

```{r}
converge_vec2[diff_subjs$id,  2]
```

And there prediction track (take the top 4):

```{r}
full_join(df_pred %>% select(id, t, Y, eta_i, pred0.4),
          df_pred2 %>% select(id, t, pred0.4),
          by = c("id", "t")) %>% 
  filter(id %in% diff_subjs$id[1:4]) %>%
    mutate_at(vars(eta_i, pred0.4.x, pred0.4.y), function(x){exp(x)/(1+exp(x))}) %>%
    ggplot()+
    geom_point(aes(x=t, y=Y), size = 0.2)+
    geom_line(aes(x=t, y=eta_i, col = "True"))+
    geom_line(aes(x=t, y=pred0.4.x, col = "unscaled"), linetype="dashed", na.rm=T)+
    geom_line(aes(x=t, y=pred0.4.y, col = "scaled"), linetype="dashed", na.rm=T)+
    facet_wrap(~id)+
    labs(title = "Maximum observation time = 0.4")
```
